### 2024-11-12 conteudo/preliminar/results.tex
add appendix for feedback
fix typo

The process of sending this patch did not yield satisfactory results in terms of 
interaction with the AMD Display driver maintainers. We initially submitted the 
patch on August 9th, 2024, but did not receive any replies. As a result, we had 
to resend it on October 9th, 2024, and finally received an initial response on 
November 3rd, 2024, from our point of contact at the AMD Display driver. 
The response time from our interactions with the AMD Display driver is making 
us reconsider the viability of our initial plans.

Regarding the patch content, only minor changes were requested to align with code 
style and best practices that were initially unknown to us. More details of the 
patch can be found in Appendix (CREATE APPENDIX AND ADD HERE).

>>>>

The process of sending the patch did not yield satisfactory results in terms of 
interaction with the AMD Display driver maintainers. We initially submitted the 
patch on August 9th, 2024, but did not receive any replies. As a result, we had 
to resend it on October 9th, 2024, and finally received an initial response on 
November 3rd, 2024, from our point of contact at the AMD Display driver. 
The response time from our interactions with the AMD Display driver is making 
us reconsider the viability of our initial plans.

Regarding the patch content, only minor changes were requested to align with code 
style and best practices that were initially unknown to us. More details of the 
patch can be found in Appendix \ref{app:feedback}.
